Finding ARG1 of Partitive Nouns in NomBank with DistilBERT

### 2022-05-05 src/paper.tex
Update

As for the partitive dataset, it is also shown by Table \ref{tab:results-on-partitive-dataset} that the DistilBERT model performs better than the MaxEnt Baseline model that achieved an F1 score of \verb|0.4364|. The basic pipeline achieved an F1 score of  \verb|0.7945|. It is also observed that the POS tags and NG-BIO tags features didn't have statistically significant improvement on the performance of the model, achieving an F1 score of only \verb|0.7916|. When compared to the \% dataset, the decrease in performance is expected since the partitive dataset has more distractions and noise. The tendency of over generating ARG1s is also observed for DistilBERT models in the partitive dataset, and can not easily be improved by forcing one ARG1, which is consistent with the observations made for the result on \% dataset shown in \ref{sec:results-first-dataset}.

@@

>>>>

As for the partitive dataset, it is also shown by Table \ref{tab:results-on-partitive-dataset} that the DistilBERT model performs better than the MaxEnt Baseline model which achieved an F1 score of \verb|0.4364|. The basic DistilBERT pipeline achieved an F1 score of  \verb|0.7945|. It is also observed that the POS tags and NG-BIO tags features didn't have statistically significant improvement on the performance of the model, achieving an F1 score of only \verb|0.7916|. Aside from that, when compared to the \% dataset, the decrease in performance is expected since the partitive dataset has more distractions and noise. The tendency of over generating ARG1s is also observed for DistilBERT models in the partitive dataset, and can not easily be improved by forcing one ARG1, which is consistent with the observations made for the result on \% dataset shown in \ref{sec:results-first-dataset}.

@@

Based on the performance decrease observed in the partitive dataset, we also concluded that the ARG1 finding pipelines are generally sensitive to the noise in the partitive dataset. However, the DistilBERT models are relatively more robust to noise with 14.26\% decrease in performance compared to the baseline MaxEnt model's 34.06\% decrease.
